---
title: "Correlation Graph, Community Detection, and Graph Manipulation"
author: "Steven Surya Tanujaya"
date: "July 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The objective here is to cluster the city in Swiss based on the given attributes using correlation network. First, we need to filter city/row with very high correlation to (at least one) other city.

This documentation can also be accessed in my Kaggle kernel, [here](https://www.kaggle.com/stevensurya/clustering-using-correlation-network)

The `corrr` package works well with `tidygraph` and `ggraph`. We will use this pacakage to 
```{r}
library(tidygraph)
library(ggraph)
library(corrr)
library(tidyverse)

##NOTE: COBA DI SCALE SEBELUM COR

swiss.cor <- swiss %>%    # t() for matrix transpose
  t() %>% correlate() %>%    # correlate() is equivalent to cor() but                                                put NA as its diagonal entry and different class
  shave(upper = TRUE) %>%            # Shave the data frame to lower triangular matrix
  stretch(na.rm = TRUE) %>%           
  filter(r >= 0.99)                 
swiss.cor
```

Here we have constructed "the edges" dataframe for mtcars dataset.

```{r}
#Create tbl_graph object
library(tidygraph)
library(ggraph)
set.seed(100)
swiss.graph <- as_tbl_graph(swiss.cor, directed = FALSE)

# There are 11 city missing, which means they have weak correlation to other city 
swiss.graph %>% activate(nodes) %>% as.data.frame() %>% nrow()
nrow(swiss)

#visualize the network
ggraph(swiss.graph) + 
  geom_edge_link() + 
  geom_node_point() +
  geom_node_text(
    aes(label = name), size = 3, repel = TRUE
    ) +
  theme_graph()
```

First, let compare the k-means result to the network components.
```{r}
set.seed(1)
swiss.clust<-kmeans(swiss,4)
```


We want to color the network by `cluster`, here we can apply `join` to graph object. 
```{r}
swiss.group <- data_frame(
  name = rownames(swiss),
  group = as.factor(swiss.clust$cluster)
)

swiss.graph <- swiss.graph %>%
  activate(nodes) %>%
  left_join(swiss.group, by = "name") %>%
  rename(label = name) %>% 
  activate(edges) %>% 
  rename(weight=r)
```

```{r}
set.seed(100)
ggraph(swiss.graph) + 
  geom_edge_link(aes(width = weight), alpha = 0.2) + 
  scale_edge_width(range = c(0.2, 1.8)) +
  geom_node_point(aes(color = group), size = 3) +
  geom_node_text(aes(label = label), size = 3, repel = TRUE) +
  theme_graph()
```

How about the negative correlation?
```{r}
swiss.cor2 <- swiss %>%    
  t() %>% correlate() %>%    
  shave(upper = TRUE) %>%           
  stretch(na.rm = TRUE) %>%           
  filter(r < 0)                 
swiss.cor

set.seed(100)
swiss.graph2 <- as_tbl_graph(swiss.cor2, directed = FALSE)

swiss.graph2 <- swiss.graph2 %>%
  activate(nodes) %>%
  left_join(swiss.group, by = "name") %>%
  rename(label = name) %>% 
  activate(edges) %>% 
  rename(weight=r)

set.seed(100)
ggraph(swiss.graph2) + 
  geom_edge_link(aes(width = -weight), alpha = 0.2) + 
  scale_edge_width(range = c(0.2, 1.8)) +
  geom_node_point(aes(color = group), size = 3) +
  geom_node_text(aes(label = label), size = 3, repel = TRUE) +
  theme_graph()
```

community detection can be applied using `group_*` some of them using edges and some using node as their calculation
```{r}
set.seed(100)
swiss.graph %>%
  activate(nodes) %>%
   mutate(community = as.factor(group_infomap())) %>% 
  ggraph(layout = "graphopt") + 
  geom_edge_link(width = 1, colour = "lightgray") +
  geom_node_point(aes(colour = community), size = 4) +
  geom_node_text(aes(label = label), repel = TRUE)+
  theme_graph()
```

This result show us better cluster for our data. Compared to k-means, this method is more reliable since it is not just only consider the value of each node but also its pattern (in this case: correlation).



Reference:   

- http://www.sthda.com/english/articles/33-social-network-analysis/136-network-analysis-and-manipulation-using-r/
